User-level Grid Monitoring with Inca 2

### 2007-02-28 pubs/papers/hpdc-gmw-2007/paper.tex
global edits - grammar changes and added citations
git-svn-id: file:///localdisk/subversion/inca/trunk/pubs@6605 7dba3f4a-8be6-0310-8b3b-b4fec25ea7f3

\item Creates and configures tests and performance measurements based on user
documentation rather than on system administrator knowledge (of hostnames,
ports, pathnames, etc.).  This may not always be possible when documentation
and tests are developed simultaneously during pre-production, but they should
be closely coordinated activities.

@@

\item Represents overall Grid status by testing a variety of 
documented user commands and individual Grid software components.

\item Automates the periodic execution of user-level tests or performance
measurements to capture dynamic Grid status.

@@

\item Measures the system impact of tests and benchmarks executing on
the monitored resources in order to tune their execution frequency to
reduce the impact on the resources. *

@@

% overview description of components
Figure~\ref{arch_fig} shows the architecture of Inca 2.
Inca 2 incorporates three core
components (highlighted box):  the agent, depot, and reporter manager.
The \textit{agent} and \textit{reporter managers} coordinate the execution of
tests and performance measurements on the Grid resources and the
\textit{depot} stores and archives the results.  The inputs to Inca 2 are one
or more \textit{reporter repositories} that contain user-level tests and
benchmarks, called \textit{reporters}, and a configuration file describing how
to execute them on the Grid resources.  This configuration is normally created
using an administration GUI tool
called \textit{incat} (Inca Administration Tool).  The output or results
collected from the resources are queried by the \textit{data consumer} and
displayed to users.  The following steps describe how an Inca administrator
would deploy user-level tests and/or performance measurements to their
resources.

@@

An extensible set of Perl APIs is provided to handle much of the effort of
writing reporters.  Figure~\ref{pingReporter} shows (a) an Inca reporter that
pings a pre-WS Globus GRAM server and (b) its corresponding output when
executed on a local machine.  The reporter uses two of the Perl APIs:
Inca::Reporter::SimpleUnit (a subclass of Inca::Reporter) and
Inca::Reporter::GridProxy.  The Inca::Reporter API provides convenience
functions for handling the required input arguments
(lines~\ref{pingReporter}(a) 12-14 produces lines \ref{pingReporter}(b)
10-31) and printing the Inca-compliant header and exit status XML tags
(lines~\ref{pingReporter}(a) 3-10, 24 produces \ref{pingReporter}(b)
1-9, 43-46).  It also includes some informational and debug logging functions
similar to log4j.  The log output has been very useful to system
administrators, who can view a summary of the test or benchmark that the
reporter performed without reading the reporter source code.  Line
\ref{pingReporter}(a) 15 shows a special log function, loggedCommand, that
executes a system command (using a 30 second timeout) after logging it to the
'system' level of the log XML (producing lines \ref{pingReporter}(b) 32-36).  The subclass
Inca::Reporter::SimpleUnit is the API responsible for printing the simplest
standard reporter body schema to report software functionality or service
tests results; it handles the printing of the small body XML
(lines~\ref{pingReporter}(b) 39-41).  Finally, the
Inca::Reporter::GridProxy dependency (line~\ref{pingReporter}(a) 11) adds a proxy
dependency to the reporter, telling Inca to download a
short-term proxy before running this reporter (as discussed in
Section~\ref{security}).  Most current reporters use the Perl APIs and consist
of fewer than 30 lines of code.

@@

% We have a lot of reporters ready to be picked 
The Inca team publishes a reporter repository that contains 143 reporters
developed and tested for TeraGrid.  Most reporters are either version
reporters that collect version information from a software package,
unit test reporters that run a more involved
functionality test, or performance benchmark reporters.  The unit and version
reporters cover software such as Grid middleware, compilers, math libraries,
data tools, and visualization tools.  Current performance reporters
measure data transfer and execute Grid benchmarks as described in
Section~\ref{grasp}.

@@

Inca was designed to distribute control and storage workload among
multiple Inca components if needed.  For example, one depot could forward
storage requests and queries to another depot to distribute its workload or to
maintain a mirror for fault tolerance.  Figure~\ref{tg_coord_fig} shows a more
complex scenario where two Inca deployments coordinate with each other.  For
example, application communities like GEON have their own Grid but also have
access to resources on TeraGrid.   Two separate Inca deployments can result in
duplicate testing. Instead, one Inca deployment can coordinate the execution
of a suite with another deployment.
Figure~\ref{tg_coord_fig} shows this type of coordinated deployment, where Grid B 
has its own resources but also has access to resources in Grid A.
When an Inca administrator submits a suite to Grid B, the Inca agent running
on Grid B will determine which reporters run on Grid A resources and forward
them as a suite request to Grid A's agent.  If Grid B has permission to submit
suites, Grid A's agent will execute the suite and configure its depot to
forwards results back to Grid B's depot.  Forwarding is not yet implemented 
in Inca 2.

@@

To provide user-level monitoring of CTSSv3, Inca was originally
deployed on TeraGrid in 2003 using Inca 1 and was transitioned to Inca 2 in
November 2006.  In addition to CTSSv3 monitoring, Inca is now also being used
to collect job usage information from Globus 2 GRAM logs and to detect expired
host and CA certificates and CA CRLs.

@@

Other Inca users include the European DEISA Grid and the UK National Grid
Service (NGS).  DEISA and NGS began using Inca in late 2004 and early 2005 respectively.  
Similar to TeraGrid, DEISA uses Inca to verify their Common
Production Environment (DCPE) across their 11 heterogeneous resources.  They
currently have 40 version reporters to verify each of the packages included in
DCPE.  In addition, they have unit reporters for the DEISA Applications Test
Suite (DATS) to check basic operation of the C/C++/Fortran compilers, the MPI
library, some numerical libraries, OpenMP jobs, CORBA middleware, and a third
party application.  DEISA is currently using Inca 1 and will transition to
Inca 2 in the next few months.

>>>>

\item Emulates a regular user by using tests and performance measurements created and configured based on user
documentation rather than on system administrator knowledge (of hostnames,
ports, pathnames, etc.).  This may not always be possible when documentation
and tests are developed simultaneously during pre-production, but they should
be closely coordinated activities.

@@

\item Provides a representative indication of Grid status by testing
documented user commands and individual Grid software components.

\item Automates the periodic execution of user-level tests or performance
measurements to understand Grid behavior over time.

@@

\item Measures the system impact of tests and benchmarks executing on
the monitored resources in order to tune their execution frequency and
reduce the impact on resources if needed. *

@@

% overview description of components
Figure~\ref{arch_fig} shows the architecture of Inca 2, which
incorporates three core
components (highlighted box):  the agent, depot, and reporter manager.
The \textit{agent} and \textit{reporter managers} coordinate the execution of
tests and performance measurements on the Grid resources and the
\textit{depot} stores and archives the results.  The inputs to Inca 2 are one
or more \textit{reporter repositories} that contain user-level tests and
benchmarks, called \textit{reporters}, and a configuration file describing how
to execute them on the Grid resources.  This configuration is normally created
using an administration GUI tool
called \textit{incat} (Inca Administration Tool).  The output or results
collected from the resources are queried by the \textit{data consumer} and
displayed to users.  The following steps describe how an Inca administrator
would deploy user-level tests and/or performance measurements to their
resources.

@@

An extensible set of Perl APIs is provided to handle much of the effort of
writing reporters.  Figure~\ref{pingReporter} shows (a) an Inca reporter that
pings a pre-WS Globus GRAM server and (b) its corresponding output when
executed on a local machine.  The reporter uses two of the Perl APIs:
Inca::Reporter::SimpleUnit (a subclass of Inca::Reporter) and
Inca::Reporter::GridProxy.  The Inca::Reporter API provides convenience
functions for handling the required input arguments
(lines~\ref{pingReporter}(a) 12-14 produces lines \ref{pingReporter}(b)
10-31) and printing the Inca-compliant header and exit status XML tags
(lines~\ref{pingReporter}(a) 3-10, 24 produces \ref{pingReporter}(b)
1-9, 43-46).  It also includes some informational and debug logging functions
similar to log4j.  The log output has been very useful to system
administrators, who can view a summary of the test or benchmark that the
reporter performed without reading the reporter source code.  Line
\ref{pingReporter}(a) 15 shows a special log function, loggedCommand, that
executes a system command (using a 30 second timeout) after logging it to the
'system' level of the log XML (producing lines \ref{pingReporter}(b) 32-37).  The subclass
Inca::Reporter::SimpleUnit is the API responsible for printing the simplest
standard reporter body schema that reports software functionality or service
tests results; it handles the printing of the small body XML
(lines~\ref{pingReporter}(b) 39-41).  Finally, the
Inca::Reporter::GridProxy dependency (line~\ref{pingReporter}(a) 11) adds a proxy
dependency to the reporter, telling Inca to download a
short-term proxy before running this reporter (as discussed in
Section~\ref{security}).  Most current reporters use the Perl APIs and consist
of fewer than 30 lines of code.

@@

% We have a lot of reporters ready to be picked 
The Inca team publishes a reporter repository that contains 143 reporters
developed and tested for TeraGrid.  Most reporters are either version
reporters that collect version information from a software package,
unit test reporters that run a more involved
functionality test, or performance benchmark reporters.  The unit and version
reporters cover software such as Grid middleware and tools, compilers, math libraries,
data tools, and visualization tools.  Current performance reporters
measure data transfer and execute Grid benchmarks as described in
Section~\ref{grasp}.

@@

Inca was designed to distribute control and storage workload among
multiple Inca components if needed.  For example, one depot could forward
storage requests and queries to another depot to distribute its workload or to
maintain a mirror for fault tolerance.  Figure~\ref{tg_coord_fig} shows a more
complex scenario where two Inca deployments coordinate with each other.  For
example, application communities like GEON~\cite{geon} have their own Grid but also have
access to resources on TeraGrid.   Two separate Inca deployments can result in
duplicate testing. Instead, one Inca deployment can coordinate the execution
of a suite with another deployment.
Figure~\ref{tg_coord_fig} shows this type of coordinated deployment, where Grid B 
has its own resources but also has access to resources in Grid A.
When an Inca administrator submits a suite to Grid B, the Inca agent running
on Grid B will determine which reporters run on Grid A resources and forward
them as a suite request to Grid A's agent.  If Grid B has permission to submit
suites, Grid A's agent will execute the suite and configure its depot to
forwards results back to Grid B's depot.  Forwarding is not yet implemented 
in Inca 2.

@@

To provide user-level monitoring of CTSS, Inca was originally
deployed on TeraGrid in 2003 using Inca 1 and was transitioned to Inca 2 in
November 2006.  In addition to CTSSv3 monitoring, Inca is now also being used
to collect job usage information from Globus 2 GRAM logs and to detect expired
host and CA certificates and CA CRLs.

@@

Other Inca users include the European DEISA Grid~\cite{deisa} and the UK National Grid
Service (NGS)~\cite{ngs}.  DEISA and NGS began using Inca in late 2004 and early 2005 respectively.  
Similar to TeraGrid, DEISA uses Inca to verify their Common
Production Environment (DCPE) across their 11 heterogeneous resources.  They
currently have 40 version reporters to verify each of the packages included in
DCPE.  In addition, they have unit reporters for the DEISA Applications Test
Suite (DATS) to check basic operation of the C/C++/Fortran compilers, the MPI
library, some numerical libraries, OpenMP jobs, CORBA middleware, and a third
party application.  DEISA is currently using Inca 1 and will transition to
Inca 2 in the next few months.
